---
title: "Simulated Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simulated Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Electronic health records (EHR) linked with biorepositories are 
a powerful platform for translational studies. A major bottleneck exists 
in the ability to phenotype patients accurately and efficiently. 
Towards that end, we developed an automated high-throughput 
phenotyping method integrating International 
Classification of Diseases (ICD) codes and narrative data extracted 
using natural language processing (NLP). Specifically, our proposed method, 
called MAP (Map Automated Phenotyping algorithm), fits an ensemble of latent 
mixture models on aggregated ICD and NLP counts along with healthcare 
utilization. The MAP algorithm yields a predicted probability of phenotype 
for each patient and a threshold for classifying subjects with phenotype 
yes/no [See Katherine P. Liao, et al. (2019](https://pubmed.ncbi.nlm.nih.gov/31613361/).

## MAP function call on example data

Here we show the example call to the MAP function. Two parameters are 
Simulate data to test the algorithm

```{r}
library(MAP)
set.seed(123)
n_patients = 400
frequency_ICD_codes = c(rpois(n_patients / 4, 10), rpois(n_patients / 4, 1), rep(0, n_patients / 2))
frequency_NLP_CUIs = c(rpois(n_patients / 4, 10), rpois(n_patients / 4, 1), rep(0, n_patients / 2))

m_data = Matrix(data = cbind(frequency_ICD_codes, frequency_NLP_CUIs), sparse = TRUE)
m_healthcare_util = Matrix(rpois(n_patients, 10) + 5, ncol = 1, sparse = TRUE)

map_fit = MAP(mat = m_data, note = m_healthcare_util)
```

```{r}
head(map_fit$scores)
```

```{r}
map_fit$cut.MAP
```
